### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

%\begin{table*}
%\centering
\caption{Existing leakage detection tool only evaluate them on cryptography library. 1. Most recent work only evaluates their approaches on cryptography libraries. 2. All of them can not reason about the total effect of multiple leakages.}
\label{table:related_work}
\resizebox{1\columnwidth}{!}{%

\begin{tabular}{lllcclc}
\toprule
Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
CacheAudit~\cite{doychev2015cacheaudit} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
CacheD~\cite{wang2017cached} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
CachSym~\cite{brotzman2019casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
CacheS~\cite{wang2019identifying} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
DATA~\cite{weiser2018data} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & Deep Learning, gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
\bottomrule
\end{tabular}
}
%\end{table*}
\end{sidewaystable}
Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

>>>>

%\begin{table*}
%\centering
\caption{Existing leakage detection tool only evaluate them on cryptography library. 1. Most recent work only evaluates their approaches on cryptography libraries. 2. All of them can not reason about the total effect of multiple leakages.}
\label{table:side_channel_detection_tool}
\resizebox{1\columnwidth}{!}{%

\begin{tabular}{lllcclc}
\toprule
Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
CacheAudit~\cite{182946} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
CacheD~\cite{203878} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
CachSym~\cite{Brotzman19Casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
CacheS~\cite{236338} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
DATA~\cite{217537} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
\bottomrule
\end{tabular}
}
%\end{table*}
\end{sidewaystable}
Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.
